Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-16 ms.qmd
Fixed figure to look better

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 7) + 
geom_text(data = dat_text, aes(x = x, y = y-0.2, label = label2), size = 7) +
geom_text(data = dat_text, aes(x = x, y = y-0.4, label = p), size = 7) +
geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 7) + 
theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))

@@

p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 7) + 
geom_text(data = dat_text2, aes(x = x, y = y-0.2, label = label2), size = 7) +
geom_text(data = dat_text2, aes(x = x, y = y-0.4, label = p), size = 7) +
theme(legend.position = "bottom", 
      strip.background = element_blank(), 
      strip.text = element_blank(), 
      axis.text = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16))

p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A", tag_suffix = ")")

ggsave(p8.1.2, width = 13, height = 12.5, filename = "./output/figures/fig8.png")

>>>>

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
geom_text(data = dat_text, aes(x = x, y = y-0.3, label = label2), size = 5) +
geom_text(data = dat_text, aes(x = x, y = y-0.6, label = p), size = 5) +
geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 5) + 
theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))

@@

p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 5) + 
geom_text(data = dat_text2, aes(x = x, y = y-0.3, label = label2), size = 5) +
geom_text(data = dat_text2, aes(x = x, y = y-0.65, label = p), size = 5) +
theme(legend.position = "bottom", 
      strip.background = element_blank(), 
      strip.text = element_blank(), 
      axis.text = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16))

p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))

ggsave(p8.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig8.png")
